DATA 621 Homework #2

### 2019-10-06 hw2/HW2.Rmd
Minor updates
More work on HW2

## Confusion Matrix

```{r}
source("hw2.R")
df <- read.csv("./data/classification-output-data.csv")
actual <- "class"
predicted <- "scored.class"

confusion_matrix(df, actual, predicted) %>%
  kable() %>%
  kable_styling()
```

## Accuracy

```{r, null_prefix=TRUE}
accuracy(df, actual, predicted)
```

## Classification Error Rate

```{r, null_prefix=TRUE}
classification_error_rate(df, actual, predicted)
```

### Verify Accuracy and Error Rate Sum to 1

```{r, null_prefix=TRUE}
accuracy(df, actual, predicted) + classification_error_rate(df, actual, predicted)
```

## Precision

```{r, null_prefix=TRUE}
precision(df, actual, predicted)
```

## Sensitivity

```{r, null_prefix=TRUE}
sensitivity(df, actual, predicted)
```

## Specificity

```{r, null_prefix=TRUE}
specificity(df, actual, predicted)
```

## F1 Score

```{r, null_prefix=TRUE}
f1_score(df, actual, predicted)
```
### F1 Score Will Always be Between 0 and 1

>>>>

```{r}
df <- read.csv("./data/classification-output-data.csv")
actual <- "class"
predicted <- "scored.class"
probability <- "scored.probability"
# Load our functions
source("hw2.R")
```

## Caret's Output

```{r}
confusionMatrix(factor(df[[predicted]]), factor(df[[actual]]))
```

## Our Function's Output

**Confusion Matrix**

```{r}
confusion_matrix(df, actual, predicted) %>%
  kable() %>%
  kable_styling()
```

**Accuracy**: `r accuracy(df, actual, predicted)`

**Classification Error Rate**: `r classification_error_rate(df, actual, predicted)`

**Precision**: `r precision(df, actual, predicted)`

**Sensitivity (Recall)**: `r sensitivity(df, actual, predicted)`

**Specificity**: `r specificity(df, actual, predicted)`

**F1 Score**: `r f1_score(df, actual, predicted)`
